\huge Tor's Usability for Censorship Circumvention

### 2016-05-08 pets2017-paper/pets2017-paper.tex
time to success redone, still not significant (but more correct).
Time to success performs a one-tailed mann-whitney U test on
two groups of participants, participants who used NEW and OLD
interfaces. DNFs were given a time to success of 40:08.
explain statistical test for active time

\subsubsection{Active Configuration Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment. The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. Logs show that participants spent 58\% of their overall time at the progress screen. 
{\color {red} discuss by environment (time on first) and by version (proxy).}
Table ~\ref{table:median_time} shows the median percentage of time spent on each screen,
computed independently for each screen.

We believe participants spent a long time on the progress screen for a combination of reasons. Even with correct configurations, the bootstrap process can take up to two minutes. With incorrect settings, we suspect that participants waited because the interface instructs them ``wait a couple minutes.'' A lack of error messages and timeouts on the progress screen, also caused some users to wait indefinitely.

\begin{table}[t]
\centering
	\begin{tabular}{c r r r r}
	& First & Proxy & Bridge & Progress \\
	\noalign{\hrule}
	All & 7\% & 5\% & 4\% & 58\% \\
	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
	E2-NEW & 5\% & 5\% & 5\% & 76\% \\
	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
	E3-NEW & 3\% & 3\% & 5\% & 73\% \\
	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
	\end{tabular}
\caption{The median percent of time participants spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage independent for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.} 
\label{table:median_time}
\end{table}

@@

\begin{table}
\centering
	\begin{tabular}{c r r}
	 & Total Active Minutes & Total \% of Overall Time \\
	\noalign{\hrule}
	All & 381 & 29\% \\ 
	E1-NEW & 4 & 45\% \\
	E1-OLD & 19 & 67\% \\
	E2-NEW & 15 & 15\% \\
	E2-OLD & 68 & 31\% \\
	E3-NEW & 74 & 18\% \\
	E3-OLD & 200 & 38\% \\
	\end{tabular}
\caption{active time {\color {red} add comparable figure to the time to success figure (Fig 9)}.} 
\label{table:active_time}
\end{table}

Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection. We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap. This is a simplified notion active configuration time. Some participants searched for help on the web after exiting the interface or on the progress screen.

{\color {red} TODO: explain how this was calculated: across all participants with all of the new and all of the old aggregated, with DNF's getting 40:08 then subtracting the time they spent on the progress screen). Say it is mann whitney one tailed. } The new interface results a statistically significant reduction in the overall active configuration time. (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$). We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)

>>>>

\subsubsection{Active Configuration Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface. With correct configurations, the bootstrap process can take up to two minutes.  With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.  Logs show that participants spent 58\% of their overall time at the progress screen. Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.

\begin{table}[t]
\centering
	\begin{tabular}{c r r r r}
	& First & Proxy & Bridge & Progress \\
	\noalign{\hrule}
	All & 7\% & 5\% & 4\% & 58\% \\
	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
	E2-NEW & 5\% & 5\% & 5\% & 76\% \\
	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
	E3-NEW & 3\% & 3\% & 5\% & 73\% \\
	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
	\end{tabular}
\caption{The median percent of time participants spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage independent for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens. Note that the time spent on the progress bar dominates the 
time spent in the interface.} 
\label{table:median_time}
\end{table}

@@

Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection. We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap. Active configuration time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes. This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.

We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface. The new interface results a statistically significant reduction in active configuration time. (Mann--Whitney $Z = -2.7$, $p = 0.0032$, $r= 0.25$). We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
